\textbf{Influence of galaxy rotation and outflows \\ in the Lyman Alpha spectral line}

### 2016-02-26 abstract/abstract.tex
minor typos

Radiative transfer MonteCarlo simulations are nowadays a required tool
to interprete the Lyman-$\alpha$ line morphology. In this work we
explore a new model that computes the join effect of outflows and
bulk rotation. The main conclusion is that rotation and a modest
outflow velocity is enough to reproduce the primary characteristics of
observed LAEs. 
We will show results of adjusting observational data for some selected
objects to models with and without bulk rotation. We finalize by
discussing the possible implications for these results in terms of the
energetics required for supernova feedback and outflows in high
redshift galaxies.

>>>>

Radiative transfer MonteCarlo simulations are nowadays a required tool
to interpret the Lyman-$\alpha$ line morphology. In this work we
explore a new model that computes the joint effect of outflows and
bulk rotation. The main conclusion is that rotation and a modest
outflow velocity is enough to reproduce the primary characteristics of
observed LAEs. 
We will show results of adjusting observational data for some selected
objects to models with and without bulk rotation. We finalize by
discussing the possible implications for these results in terms of the
energetics required for supernova feedback and outflows in high
redshift galaxies.
